Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-08 numerical-mhd-ct.tex
More edits to fluid section - done?
Minor change to MHDCT

\subsection{MHD: Constrained transport}
\label{sec.num.mhd-ct}
\def\Bvec{{\bf B}}
\def\Bf{Bf}
\def\Bc{Bc}
\def\Evec{{\bf E}}
\def\Divb{\ensuremath{\div \Bvec}}

The third solver we describe is an MHD method developed by 
\citet{Collins10} in order to study Population
III stars \citep{Xu08}, molecular clouds \citep{Collins12a}, and galaxy clusters
\citep{Xu12, Skillman13}.  A full description and suite of test problems can be
found in \citet{Collins10} and therefore we only describe the method briefly.

@@

Cosmological MHD can be treated in a number of ways.  As described in 
the previous section, and equation~\ref{eq:induction} the MUSCL with Dedner
method treats the cosmological dilution of
$\vecB$ with a source term,  However, one can eliminate the right hand side of Equation 
\ref{eq:induction} by defining
$\vecB^\prime = \vecB / \sqrt{a}.$
Then equation~\ref{eq:induction} becomes
$$ 
\frac{\partial \vecB^\prime}{\partial t} - \frac{1}{a}  \curl (\vecv \times
\vecB^\prime)  = 0, \label{eq:induction_cosmo_prime_nosource}
$$
and we can reuse each part of the non-cosmological algorithm (hyperbolic solver,
electric field creation, interpolation, projection, and flux correction) without
modification.

>>>>

\subsection{Magnetohydrodynamics: Constrained transport}
\label{sec.num.mhd-ct}
\def\Bvec{{\bf B}}
\def\Bf{Bf}
\def\Bc{Bc}
\def\Evec{{\bf E}}
\def\Divb{\ensuremath{\div \Bvec}}

The third solver we describe is an MHD method developed by 
\citet{Collins10} and since a full description and suite of test problems can be
found in that paper, we only describe the method briefly here.

@@

Cosmological MHD can be treated in a number of ways.  As described in 
the previous section, and equation~\ref{eq:induction} the MUSCL with Dedner
method treats the cosmological dilution of
$\vecB$ with a source term,  However, one can eliminate the right hand side of equation 
\ref{eq:induction} by defining
$\vecB^\prime = \vecB / \sqrt{a}.$
Then equation~\ref{eq:induction} becomes
$$ 
\frac{\partial \vecB^\prime}{\partial t} - \frac{1}{a}  \curl (\vecv \times
\vecB^\prime)  = 0, \label{eq:induction_cosmo_prime_nosource}
$$
and we can reuse each part of the non-cosmological algorithm (hyperbolic solver,
electric field creation, interpolation, projection, and flux correction) without
modification.
